Argennon: A Scalable Cloud Based Smart Contract Platform

### 2022-07-24 tex/A.tex
Fix a minor error
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>
Update abstract
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

\begin{document}
    \maketitle
    \begin{abstract}
        Argennon is a next generation cloud based blockchain and smart
        contract platform. The Argennon blockchain uses
        a hybrid proof of stake (HPoS) consensus protocol, which is capable of combining the benefits of
        a centralized and a decentralized system. Thanks to the cloud
        based design of the Argennon blockchain, transaction validation does not require costly
        computational resources, and normal personal computers or smartphones, with limited hardware capabilities, can
        validate transactions and actively
        participate in the Argennon consensus protocol. This property makes Argennon a truly decentralized and
        democratic blockchain and one of the most secure existing platforms.

@@

        By using cryptographic accumulators, the integrity of data on the Argennon cloud is guaranteed, and there
        is no need for trusting cloud servers. At the same time, by using a smart clustering algorithm the network usage
        and the overhead of the cryptographic commitment scheme is kept manageable.
    \end{abstract}
    \tableofcontents

>>>>

\begin{document}
    \maketitle
    \begin{abstract}
        Argennon is a next generation cloud based blockchain and smart
        contract platform. The Argennon blockchain uses
        a hybrid proof of stake (HPoS) consensus protocol, which is capable of combining the benefits of
        a centralized and a decentralized system. Argennon validators do not store the blockchain state and
        transaction validation does not require costly
        computational resources. In Argennon, normal personal computers or smartphones, with limited hardware
        capabilities, can validate transactions and actively
        participate in the Argennon consensus protocol. This property makes Argennon a truly decentralized and
        democratic blockchain and one of the most secure existing platforms.

@@

        By using cryptographic accumulators, the integrity of data on the Argennon cloud is guaranteed, and there
        is no need for trusting cloud servers. At the same time, by using a smart clustering algorithm the network usage
        and the overhead of the cryptographic proofs is kept manageable.
    \end{abstract}
    \tableofcontents
